---
title: "Homework 8"
output: 
  html_notebook:
  toc: yes
  toc_float: yes
author: Wenlong Li
---
### 2.1-a-i
#### I want to omit "Name" attributes
### 2.1-a-ii
#### No standardization is required, their properties are of the same type, and their values are not very different
### 2.1-a-iii
```{r}
library(dplyr)
rm(list=ls())

# Set working directory as needed
setwd("./")
con <- file("./file19.txt", "r")
line=readLines(con,n=1)
isAddTable = FALSE
table <- matrix(nrow = 0, ncol = 9)
while( length(line) != 0 ) {
     if(grepl(pattern = "Name",x = line) && !grepl(pattern = "#",x = line)){
       isAddTable = TRUE
     }
     if(isAddTable){
       line <- gsub('\"',"",line)
       str <- ""
       for(item in unlist(strsplit(line,split = " "))){
         if(nchar(item) > 1 && !grepl(pattern = " ",x = item)){
           splictStr <- ""
           if(nchar(str)>0){
             splictStr <- " "
           }
           str <- paste0(str,splictStr,item)
         }else if(nchar(item) == 1 && !grepl(pattern = " ",x = item)){
           str <- paste0(str,",",item)
         }
       }
       if(grepl(pattern = "Name",x = line)){
         colnames(table) <- unlist(strsplit(str,split = ","))
       }else{
         table <- rbind(table, unlist(strsplit(str,split = ",")))
       }
     }
     line=readLines(con,n=1)
}
close(con)
df <- data.frame(table)
# 转换数据类型
for(item in colnames(table)){
  if(!grepl(pattern = "Name",x = item)){
    df[item] = as.integer(unlist(df[item]))
  }
}
write.table(df, "./dfile.txt", row.names = FALSE, col.names = TRUE, sep = ",")
```
### 2.1-b-i
```{r}
library(cluster)
library(factoextra)
fviz_nbclust(select(df, -Name), kmeans, method="wss")
```
#### k = 3
### 2.1-b-ii
```{r}
k <- kmeans(select(df, -Name), centers=8, nstart=25)  
fviz_cluster(k, data=select(df, -Name))
```
### 2.1-b-iii
#### K-means clustering with 8 clusters of sizes 8, 11, 10, 1, 2, 8, 17, 9
### 2.1-b-iv
#### The total SSE of the clusters is 62.065983
### 2.1-b-v
#### Within cluster sum of squares by cluster:3.875000  5.454545 21.100000  0.000000  3.000000  6.375000 20.705882  1.555556
### 2.1.b-vi
```{r}
for (n in 1:8) {
  print(select(df,Name)[which(k$cluster == n),]) 
}
```
#### Most classifications are reasonable, each cluster is the same type of animals, but some classifications are not accurate

### 2.2-a
```{r}
remove(df)
df <- read.csv("./s1.csv")
```

#### Standardization is not required, and x and y are basically at the same level
### 2.2-b-i
```{r}
plot(df)
```
### 2.2-b-ii
#### From the figure, you can see 15 groups, not completely separated, several groups are connected

### 2.2-c-i
```{r}
fviz_nbclust(df, kmeans, method="wss")
```
#### The optimal number of clusters is 7
### 2.2-c-ii
```{r}
fviz_nbclust(df, kmeans, method="silhouette")
```
#### #### The optimal number of clusters is 8
### 2.2-c-iii
#### The optimal number of clusters is 8
### 2.2-d-i
```{r}
k <- kmeans(df, centers=8, nstart=25)
fviz_cluster(k, data=df)
```
### 2.2-d-ii
#### Clustering works poorly, merging some similar clusters
### 2.2-e-i
#### The value of MinPts is 4. Original dbscan used minPts = 4; suffices for 2 dimensions
### 2.2-e-ii
```{r}
library(dbscan)
dbscan::kNNdistplot(df, k =  4)
abline(h = 20000, lty = 2)

db <- fpc::dbscan(df, eps = 20000, MinPts = 4)
fviz_cluster(db, df, stand = FALSE, ellipse = F, geom = "point")
print(db)
```


