---
title: "CS 422"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
author: Wenlong Li
---

### Part 2.1-a

```{r}
options(digits=2)
setwd("./")
df = read.csv('us-covid-deaths.csv', sep = ',', header = T)
df = df[complete.cases(df),]
top6DF = df[1:6,]
print(top6DF)
```
### Part 2.1-B
```{r}
library('psych')
pairs.panels(df)
```
### Part 2.1-B.i
#### The highest positive correlation with total_tests, the correlation coefficient is 0.99
### Part 2.1-B.ii
####  the highest negative correlation with stringency_index, the correlation coefficient is -0.66
### Part 2.1-B.iii
#### 1.The higher the stringency_index, the lower the scope of the virus infection, and the lower the total_deaths will be
#### 2.The more total_tests, the more deaths will be found, and the higher total_deaths will be

### Part 2.1-C
```{r}
library("dplyr")
model <- lm(formula = total_deaths ~ ., data = select(df, -date))
summary(model)
```
### Part 2.1-D
#### this a good linear regression model.  F-statistic > 1, at least one of the predictors is useful in predicting the response. R-squared is relatively large, indicating that the model fits better.

### Part 2.1-E
#### icu_patients, total_tests, reproduction_rate, stringency_index, positive_rate

### Part 2.1-F
#### hosp_patients, The p-value for hosp_patients appears to imply that there may not be a relationship between hosp_patients and total_deaths

### Part 2.1-G
```{r}
model <- lm(formula = total_deaths ~ ., data = select(df, -date, -total_tests))
summary(model)
```









